---
title       : Data Product Project
subtitle    : Data Science Specialization
author      : Gabriel Almeida
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Data product Project

### Number of poor houses in Brazil

The proposital is evaluate the variation os brazilians poor house since 1976. Data is download from IPEA web site and plotted a regression line. 

--- .class #id 

## Data

### Example of raw data and summary:
```{r, echo=FALSE}
data[1:5,]
summary(data)
```

--- .class #id 

## Graphic

It's a simple plot command (year x number of houses) and added a regression line.

```{r, echo=TRUE, eval=FALSE}
plot(data2$Date ,data2$Number.of.poor.houses/1000000 ,type = "l", xlab="YEAR", ylab="NUMBER OF HOUSES (MILLIONS)")
            regline <- lm(data2$Number.of.poor.houses/1000000 ~ data2$Date, data=data)
            abline(regline, col="red")
```

--- .class #id 

## Slider 

Slider helps to evaluated how the number of poors houses and the regression variated over the years. 

```{r, echo=TRUE, eval=FALSE}
sliderInput('year', 'Select bottom year',value=1990, min=1976 ,max=2009 , step=1),
```





